Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX Format

### 2015-08-25 sig-alternate.tex
Gaze and PCA-error results & System diagram

We propose a adaptive model based solution to approach head pose estimation that finds correspondences between facial landmarks points and their respective locations in a face model. We use the open-source library dlib\footnote{http://dlib.net} \cite{dlib09}, to detect and extract the skeleton of the subject's face and then, use the obtained landmarkers to calculate the head pose orientation estimation. In this way, we can estimate what the subject was looking at and obtain a 3D scene representation as it is executed as a ROS (Robot Operating System) node that can be seen in figure \ref{rviz}. Compared to intrusive hardware like head mounted displays, eye-trackers, wearables for instance, this approach has a clear advantage of simplicity and integration with robotic systems, but also becomes accurate enough for general purposes in face-to-face interactions. In addition, it allows as to model complex environments, handling different number and positions of participants in the scene.

@@

Figure~\ref{realSetup} illustrates our general experimental setup: a
face-to-face child-robot interaction with an (autonomous) Aldebran's {\sc nao}
robot.

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\columnwidth]{realSetup}
    \caption{\small Our experimental setup: face-to-face interaction with a {\sc
            nao} robot.  The robot writes on the tactile tablet, the child then
            corrects the robot by directly overwriting its letters on the tablet
            with a stylus. An adult (either a therapist or an experimenter,
            depending on the studies), remains next to the child to guide the work. 
            A second tablet allows to choose demonstrations and the camera captures the subject's face.}
    \label{realSetup}
\end{figure}

A tactile tablet (with a custom application) is used for both the robot and the child to write: during a typical round, the child requests the robot to write something (a single letter, a number or a full word), and push the tablet towards the robot, the robot writes on the tablet by gesturing the writing (but without actually physically touching the tablet), the child then pull back the
tablet, corrects the robot's attempt by writing him/herself on top or next to the robot's writing (see Figure~\ref{fig:diego}), and ``send'' his/her demonstration to the robot by pressing a small button on the tablet. The robot ``learns'' from this demonstration and tries again.

@@

\begin{table}[h!]
	\centering
	\caption{Tracking accuracy in face-to-face scenario}
	\begin{tabular}{|c|c|c|c|c|c|c|c|} \hline
	\small Subject & 1 & 2 & 3 & 4 & 5 & 6 & Avg\\ \hline
	\small Track(\%) & \small78.7 & \small81.1 & \small73.7 & \small75.6 & \small77.1 & \small68.7 & \small75.8 \\ \hline
	\begin{tabular}{@{}c@{}}\small Real vs \\ \small expected(\%)\end{tabular} & \small93.1 & \small  & \small & \small & \small & \small & \small \\ \hline
	\begin{tabular}{@{}c@{}}\small Real vs \\ \small captured(\%)\end{tabular} & \small59.4 & \small & \small & \small & \small & \small & \small \\ \hline
	\begin{tabular}{@{}c@{}}\small Cosine \\ \small affinity \end{tabular} & \small0.72 & \small & \small & \small & \small & \small & \small \\ \hline
	\end{tabular}
	\label{tab:results}
\end{table}

@@

\begin{figure*}
    \centering
    \includegraphics[width=1.8\columnwidth]{realExpected}
    \caption{\small In blue, real VFOA accoding to two observer's assessment. In cyan, the matching between the real and the obtained VFOA. In yellow, the repeated pattern in turn-taking and in orange, the experimenter's suggestion to choose a new word.}
    \label{fig:realExpected}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{kmeans}
    \caption{\small K-means clustering of the VFOA.}
    \label{kmeans}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=1.81\columnwidth]{realCaptured}
    \caption{\small Real VFOA accoding to two observer's assessment. In green, the obtained VFOA using our aproach and in cyan, the mathing between them. Finally, the correspondent numbers with figure \ref{fig:bitmap}.}
    \label{fig:realCaptured}
\end{figure*}

@@

% Still under construction
\section{Conclusions}
The rate of attention shift can predict retained learning. If we consider the gaze shift within the feedback episodes, it is possible to distinguish between long and short based on the number of previous repetitions playing with the same word.
%Plot -> Support this with a plot averaging all interactions of all subjects
%Plot -> Time gets reduced at the same time correctness improves

>>>>

We propose a adaptive model based solution to approach head pose estimation that finds correspondences between facial landmarks points and their respective locations in a face model. We use the open-source library dlib\footnote{http://dlib.net} \cite{dlib09}, to detect and extract the skeleton of the subject's face and then, use the obtained landmarkers to calculate the head pose orientation estimation (see figure \ref{system}). In this way, we can estimate what the subject was looking at and obtain a 3D scene representation as it is executed as a ROS (Robot Operating System) node that can be seen in figure \ref{rviz}. Compared to intrusive hardware like head mounted displays, eye-trackers, wearables for instance, this approach has a clear advantage of simplicity and integration with robotic systems, but also becomes accurate enough for general purposes in face-to-face interactions. In addition, it allows as to model complex environments, handling different number and positions of participants in the scene.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{system}
    \caption{\small System overview showing the most relevant components involved in the estimation.}
    \label{system}
\end{figure}

@@

Figure~\ref{fig:realSetup} illustrates our general experimental setup: a
face-to-face child-robot interaction with an (autonomous) Aldebran's {\sc nao}
robot.

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\columnwidth]{realSetup}
    \caption{\small Our experimental setup: face-to-face interaction with a {\sc
            nao} robot.  The robot writes on the tactile tablet, the child then
            corrects the robot by directly overwriting its letters on the tablet
            with a stylus. An adult (either a therapist or an experimenter,
            depending on the studies), remains next to the child to guide the work. 
            A second tablet allows to choose demonstrations and the camera captures the subject's face.}
    \label{fig:realSetup}
\end{figure}

A tactile tablet (with a custom application) is used for both the robot and the child to write: during a typical round, the child requests the robot to write something (a single letter, a number or a full word), and push the tablet towards the robot, the robot writes on the tablet by gesturing the writing (but without actually physically touching the tablet), the child then pull back the
tablet, corrects the robot's attempt by writing him/herself on top or next to the robot's writing, and ``send'' his/her demonstration to the robot by pressing a small button on the tablet. The robot ``learns'' from this demonstration and tries again.

@@

\begin{table}[h!]
	\centering
	\caption{Tracking accuracy in face-to-face scenario}
	\begin{tabular}{|c|c|c|c|c|c|c|c|} \hline
	\small Subject & 1 & 2 & 3 & 4 & 5 & 6 & Avg\\ \hline
	\small Track(\%) & \small88.2 & \small83.5 & \small90.5 & \small83.1 & \small87.9 & \small85.0 & \small \\ \hline
	\begin{tabular}{@{}c@{}}\small Real vs \\ \small expected(\%)\end{tabular} & \small92.6 & \small88.8  & \small95.8 & \small93.1 & \small96.5 & \small89.6 & \small \\ \hline
	\begin{tabular}{@{}c@{}}\small Real vs \\ \small captured(\%)\end{tabular} & \small61.1 & \small85.5 & \small80.8 & \small62.2 & \small63.4 & \small83.9 & \small \\ \hline
	\begin{tabular}{@{}c@{}}\small Cosine \\ \small affinity \end{tabular} & \small0.73 & \small0.82 & \small0.87 & \small0.73 & \small0.77 & \small0.92 & \small \\ \hline
	\end{tabular}
	\label{tab:results}
\end{table}

@@

\begin{figure*}
    \centering
    \includegraphics[width=1.8\columnwidth]{realExpected}
    \caption{\small In blue, real VFOA of subject 4 accoding to two observer's assessment. In cyan, the matching between the real and the obtained VFOA. In yellow, the repeated pattern in turn-taking and in orange, the experimenter's suggestion to choose a new word.}
    \label{fig:realExpected}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{kmeans}
    \caption{\small K-means clustering of the head movements.}
    \label{kmeans}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=1.81\columnwidth]{realCaptured}
    \caption{\small Real VFOA of subject 4 accoding to two observer's assessment. In green, the obtained VFOA using our aproach and in cyan, the mathing between them. Finally, the correspondent numbers with figure \ref{fig:bitmap}.}
    \label{fig:realCaptured}
\end{figure*}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{errorR}
    \caption{\small .}
    \label{errorR}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{gazeR}
    \caption{\small .}
    \label{gazeR}
\end{figure}

% Still under construction
\section{Conclusions}
The rate of attention shift can predict retained learning. If we consider the gaze shift within the feedback episodes, it is possible to distinguish between long and short based on the number of previous repetitions playing with the same word.
%Plot -> Support this with a plot averaging all interactions of all subjects
%Plot -> Time gets reduced at the same time correctness improves -> Did not show any good results
%Plot -> Difference in gaze during feedback from a subject's whose learning is assimilated vs a one is not: The second shows more intermitent tablet-selection gaze directions.
%Diagram dlib/ROS/launch/nodes/params_ini/txt_model_face
